\section{Abstract}\label{abstract}

\textcolor{red}{The Drake Equation's longevity term, $L$, is traditionally treated as a continuous span of technosignature emission, yet real civilizations may cycle between active and dormant states due to resource depletion, systemic collapse, or other disruptions. We model collapse-recovery dynamics across ten plausible futures for Earth-originating civilization using a hybrid deterministic-stochastic framework that simulates technological growth, resource depletion, and stochastic hazards over a 1000-year window. From 200 Monte Carlo simulations per scenario, we compute duty cycles ($D_c$) ranging from $\sim$0.38 to 1.00, with most scenarios exhibiting significant intermittency. We introduce an effective detectability duration, $L_{\mathrm{eff}} = D_c \, T_{\mathrm{span}}$, and an extended formulation incorporating technosignature persistence beyond active periods. We show that technological remnants from collapsed civilizations may exhibit their own ON-OFF dynamics, creating layered duty-cycle structures. Our results suggest that the Great Silence may reflect the prevalence of low-duty-cycle civilizations rather than the rarity of intelligent life. When combined with power-law longevity distributions disfavoring long-lived technosignatures, the duty-cycle framework implies a doubly diminished probability of detection. We also discuss implications for Earth's own civilizational resilience, showing how investments in knowledge preservation, genetic resource vaults, and distributed infrastructure map onto model parameters that increase the duty cycle.}
