\section{Conclusions}

\textcolor{red}{We have developed a hybrid deterministic-stochastic model to simulate collapse-recovery dynamics across ten plausible futures for Earth-originating civilization, and used these simulations to quantify the duty cycles and effective detectability durations of technological civilizations. Our principal findings are as follows.}

\textcolor{red}{First, collapse-recovery dynamics produce a wide range of duty cycles across plausible civilizational futures. Among the ten scenarios, the mean duty cycle $D_c$ spans from approximately 0.38 (Living with the Land, S4) to 1.00 (Golden Age, S3; Out of Eden, S10), with most scenarios exhibiting significant periods of dormancy or collapse. This variability has direct implications for the probability of detecting extraterrestrial technosignatures at any given moment.}

\textcolor{red}{Second, the effective detectability duration $L_{\mathrm{eff}} = D_c \, T_{\mathrm{span}}$ provides a more realistic replacement for the traditional Drake Equation's static longevity term $L$. By incorporating the fraction of time a civilization is actually active, this formulation accounts for the intermittent nature of technosignature emission and helps reconcile theoretical predictions with the observed absence of extraterrestrial signals. When combined with recent work suggesting that technosignature longevities follow power-law distributions disfavoring long-lived signals \citep{Balbi2024-bg}, the duty-cycle framework implies a doubly diminished probability of detection for most civilizations.}

\textcolor{red}{Third, technological remnants from collapsed civilizations may exhibit their own ON-OFF dynamics, creating layered duty-cycle structures that extend the effective detectability window beyond active civilizational periods. This nuance modifies the persistence term in our extended formulation and suggests that even dormant civilizations may intermittently produce detectable signatures through autonomous remnant systems.}

\textcolor{red}{Fourth, the duty-cycle framework has implications beyond SETI. Applied to Earth's own trajectory, it provides a quantitative lens for evaluating investments in civilizational resilience---knowledge preservation archives, genetic resource vaults, and distributed infrastructure---as interventions that raise the recovery fraction $r_f$ and lower the recovery delay $r_d$, thereby increasing humanity's own duty cycle.}

\textcolor{red}{Several avenues for future work emerge from this study. Incorporating exergy constraints and non-linear growth functions informed by thermodynamic limits to growth \citep{Haqq-Misra2025-lum} could yield more physically grounded simulations. Modeling the independent duty cycles of technological remnants and their interaction with civilizational recovery would add further realism. Finally, extending the framework to account for multiple co-existent technology-producing species or for feedback between technological capacity and accessible resource stocks would broaden its applicability to non-terrestrial contexts.}

\textcolor{red}{This manuscript is fully reproducible: figures are programmatically generated, sources are modularized, and builds are automated with \texttt{latexmk}.}
