\section{Implications for Earth's Future}\label{earth-implications}

A key insight from our modeling is that the parameters governing recovery (the recovery fraction $r_f$ and the recovery delay $r_d$) are not fixed properties of a civilization but can be deliberately engineered. Investments in civilizational continuity infrastructure directly map onto these parameters: a higher $r_f$ corresponds to greater preservation of knowledge, technology, and resources through collapse events, while a lower $r_d$ corresponds to faster institutional and technological rebuilding. Together, improvements in these parameters increase the duty cycle $D_c$ and thus,increase the fraction of time civilization remains functional and productive.

The concept of "recovery kits" (curated repositories of essential knowledge designed to accelerate post-collapse rebuilding) represents one practical approach to raising $r_f$. \citet{Dartnell2014-tk} has explored in detail the minimum knowledge base required to reconstruct industrial civilization from scratch, spanning agriculture, materials science, medicine, power generation, and communication. Such recovery kits, whether physical or digital, function as a form of civilizational insurance: they ensure that the knowledge accumulated over centuries of development is not lost when institutional continuity is broken. Ongoing efforts in biological resource preservation serve as real-world examples of resiliance infrastructure in action. The Svalbard Global Seed Vault, which now holds over one million seed samples from nearly every country on Earth \citep{Asdal2020-sv}, preserves agricultural biodiversity against civilizational disruption, ensuring that post-collapse societies retain access to the genetic resources needed to rebuild food systems. More recently, Colossal Biosciences has established a BioVault in Dubai dedicated to preserving broader biodiversity through cryopreservation of cellular material from threatened species \citep{Colossal2024-bv}. In the language of our model, these vaults serve to increase $r_f$ by preserving critical biological capital through collapse events.

Several other model inputs correspond to actionable levers for resilience policy. The depletion rate $\delta$ reflects the pace at which a civilization exhausts its resource base. Circular economy principles, renewable energy transitions, and efficiency improvements all serve to reduce $\delta$, extending the time before resource-driven collapse. This connects directly to recent work reframing civilizational growth in terms of thermodynamic efficiency and exploration-exploitation trade-offs \citep{Haqq-Misra2025-lum}. A civilization that pursues spatial expansion of its resource domain (exploration) effectively lowers its per-domain $\delta$, while one that intensifies extraction within a fixed domain (exploitation) increases it. The existential hazard rate $h$ can be reduced through investments in planetary defense (e.g., asteroid deflection programs such as NASA's Double Asteroid Redirection Test, which successfully demonstrated kinetic impact as a viable deflection strategy \citep{Daly2023-dart}), pandemic preparedness, AI safety research, and nuclear risk reduction, the last of which has been shown capable of triggering global famine affecting over five billion people through climate disruption alone \citep{Xia2022-nw}. \citet{Ord2020-tp} provides a systematic assessment of existential risks and argues that humanity's current exposure to catastrophic hazards is historically anomalous and reducible through deliberate policy. In our model, even small reductions in $h$ can significantly decrease the frequency of stochastic collapse events, particularly for scenarios like S1 and S6 where exogenous hazards are a primary driver of instability. The collapse survival fraction $c_f$ can be raised through distributed and redundant infrastructure. Decentralized energy grids, mesh communication networks, and dispersed governance structures all ensure that more technological capacity survives a systemic disruption. Finally, while the initial resource stock $R_0$ is treated as exogenous in our model, in practice it can be expanded through technologies that unlock previously inaccessible resources (e.g. asteroid mining, deep ocean extraction, nuclear fusion), effectively shifting a civilization into a lower resource-pressure regime.

Viewed through the duty-cycle framework, the question of civilizational resilience becomes quantifiable: what is the marginal improvement in $D_c$ from a given resilience investment? As our parameter sensitivity analysis of S8 demonstrates (Section~\ref{monte-carlo-outcomes-and-temporal-profiles}), modest shifts in $r_f$ alone can qualitatively alter a civilization's long-term trajectory. This suggests that targeted resilience investments could yield disproportionate returns in civilizational continuity, and that the duty-cycle framework provides a practical metric for evaluating such investments.

More broadly, our results help reconcile seemingly contradictory perspectives on civilizational longevity. One view posits that technological civilizations are fundamentally fragile and prone to self-destruction soon after emergence, driven by ecological, behavioral, or structural instabilities \citep{Vinn2024-pi}. Another suggests that once civilizations surpass key thresholds of resilience and coordination, they may persist indefinitely, steadily accumulating across cosmic time \citep{Grinspoon2009-cg}. Both patterns emerge naturally in our simulations. Scarcity-driven, hierarchically governed scenarios frequently enter collapse-recovery cycles, resulting in low duty cycles. In contrast, post-scarcity, distributed scenarios maintain stable resource use and continuous activity. These differences arise not from exogenous shocks, but from internal sociotechnical structure---suggesting that the long-term fate of a civilization is shaped by the interplay of its governance structure, resource management, and resilience infrastructure.
