\section{Introduction}\label{introduction}

One of the most puzzling questions in astrobiology is whether intelligent civilizations exist elsewhere in the galaxy, and if so, why we have not yet detected them. This apparent contradiction, often referred to as the Fermi Paradox or the Great Silence, raises the question of why, in a galaxy billions of years old, we observe no clear signs of advanced extraterrestrial life. Many solutions have been proposed to explain this Great Silence \citep{Webb2010-vi}. One class of explanations suggests that intelligent life is intrinsically rare, perhaps requiring an improbable convergence of planetary, chemical, or biological conditions \citep{Wesson1990-xi}. Another contends that while intelligence may emerge, technological civilizations are typically short-lived, succumbing to self-destruction through ecological collapse, conflict, or other systemic instabilities \citep{Vinn2024-pi}.

\textcolor{red}{Regardless of which class of explanation is correct, the duration that a civilization (or its technosignatures) persists is the critical variable. Longevity has been recognized as the key factor in the search for technosignatures \citep{Balbi2021-bc}, but the longevity of a technosignature can be almost entirely separable from the age of the civilization that produces it: artifacts, atmospheric signatures, and orbital debris can persist long after their creators are gone, while active transmissions may cease well before a civilization itself does \citep{Balbi2021-bc}. Moreover, the temporal distribution of civilizations matters as much as their abundance. The detectability requirement imposes strict constraints on the epoch of appearance and communicating lifespan, so that only a small fraction of civilizations would overlap with our observational window \citep{Balbi2018-fp}. Understanding civilizational longevity therefore requires understanding the temporal dynamics of technological activity itself.}

\textcolor{red}{Most treatments of longevity assume that once a civilization becomes technologically active, it remains so continuously until it either dies out or deliberately goes silent. However this assumption is difficult to justify. Historical studies of Earth's civilizations reveal cycles of rise and fall with typical durations on the order of centuries \citep{Shermer2002-oi}, and there is no strong reason to assume that extraterrestrial technological civilizations would be exempt from similar dynamics. It has been argued that planetary civilizations face a fundamental bifurcation. Either they reach "asymptotic burnout", in which superlinear growth leads to singularity-driven collapse, or "homeostatic awakening", in which a civilization deliberately curbs expansion to achieve long-term equilibrium \citep{Wong2022-hv}. Sustainability constraints make exponential expansion highly unlikely, so advanced societies may stabilize or collapse before spreading across the Galaxy \citep{Haqq-Misra2009-jb}. If collapse is common and recovery uncertain, then the technosphere (the totality of a civilization's technological infrastructure and output) may best be understood not as a permanent state but as an intermittent phenomenon, with concrete implications for both the search for technosignatures and for understanding our own civilizational trajectory.}

\textcolor{red}{If a civilization alternates between active and dormant states, its technological output is characterized not by its total lifespan but by its \emph{duty cycle}: the fraction of time it is actively producing observable technosignatures. The concept of intermittent signals is not new to SETI---signals may be intermittent due to power conservation, planetary rotation, or targeted sequential transmissions \citep{Gray2020-cn,Gray2021-jd}. But beyond signal-level intermittency, there is a deeper, civilizational-level intermittency driven by collapse-recovery dynamics. Recent work applying Lindy's law to technosignature longevities suggests that first-detected technosignatures are likely to be short-lived rather than long-lived, with power-law distributions disfavoring persistent signals \citep{Balbi2024-bg}, reinforcing the importance of understanding intermittency at all timescales.}

\textcolor{red}{In this paper, we develop a framework that connects civilizational collapse-recovery dynamics to technosignature duty cycles. Building on a recently proposed set of ten plausible futures for Earth-originating civilization spanning 1000 years \citep{Haqq-Misra2025-rt}, we construct a hybrid deterministic-stochastic model that simulates the long-term evolution of technological capacity and resource stocks under varying governance structures, resource regimes, and hazard exposures. Collapse and recovery cycles emerge naturally from the feedback between growth and depletion, combined with stochastic existential risk. From these simulations, we compute the average duty cycle of each scenario and derive an effective detectability duration, $L_{\mathrm{eff}}$, that captures the operational reality of civilizations that switch between active and dormant states. We then explore the implications of this duty-cycle framework for the Drake Equation's longevity term \emph{L} and consider what these dynamics imply for Earth's own civilizational resilience.}
