\section{Limitations}\label{limitations}

Several limitations warrant discussion. Our modeling framework is grounded in Earth-originating scenario typologies, drawing from narrative futures methodologies informed by contemporary geopolitical, ecological, and technological trends. These projections embed assumptions about governance structures, resource constraints, and recovery dynamics that may not extend to non-terrestrial civilizations or to those that do not follow Earth-like developmental pathways. While this grounding enables empirical plausibility, it limits extrapolation beyond our biosphere's trajectory \citep{Rubin2001-sk,Denning2011-fj}. Our simulations assume bounded planetary systems and do not account for galactic colonization, interstellar migration, or modes of expansion that could alter the spatial and temporal visibility of civilizations \citep{Walters1980-ev,Papagiannis1983-xv}. We also exclude the effects of cultural convergence, information saturation, or technological transcendence (e.g., the emergence of post-biological intelligence), all of which could suppress or qualitatively change technosignature output. Our operational definition of detectability (based on internal sociotechnical continuity) does not differentiate among specific technosignature classes (e.g., radio emissions, waste heat, megastructures), nor does it address detection thresholds or instrumental sensitivity.

Additionally, our assumption that technological capacity increases linearly each year according to a fixed growth rate $r$ is a significant simplification. The many discontinuities implied by the scenarios (not only collapse points but also radical transformation points such as the emergence of artificial general intelligence or breakthroughs in energy harvesting) suggest that a linear growth model may not adequately capture the dynamics of technological change across all regimes. Moreover, the available resource stock $R_0$ is treated as an exogenous parameter, but in practice it is contingent on the technological capacity to identify and utilize resources. For example, a civilization that develops asteroid mining or nuclear fusion effectively increases its accessible resource base, fundamentally altering the growth-depletion dynamics. Recent work by \citet{Haqq-Misra2025-lum}, which shares the same ten-scenario framework employed here, reframes the Kardashev scale as a luminosity limit constrained by thermodynamic efficiency (exergy) and explores exploration-exploitation trade-offs for long-lived technospheres. Their framework shows that growth trajectories depend on whether a civilization pursues spatial expansion (exploration) or intensive resource use within a fixed domain (exploitation), a distinction that our linear growth model does not capture. Future work could incorporate exergy constraints and non-linear growth functions informed by their luminosity-limit model, as well as feedback between technological capacity and accessible resource stocks, to produce more physically grounded projections of civilizational trajectories.
